Printer ballistics through texture analysis of characters

### 2013-11-28 Printer_Ballistics.tex
Fumada do Gabriel

%%% PREAMBLE - Do not touch %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,twocolumn,letterpaper]{article}
%%\usepackage[ansinew]{inputenc}
\usepackage[latin1,utf8]{inputenc}
\usepackage[portuges,brazil,english]{babel}
\usepackage{model}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\input{abaco}

@@

\begin{table}
\label{tab:printers}
\caption{Printers used in this work}
\begin{center}
\begin{tabular}{l*{2}{c}r}
Printer           & Documents \\
\hline
Brother-HL4070CDW & 28 \\
Canon-D1150 & 28 \\
Canon-MF3240 & 28 \\
Canon-MF4370DN & 28 \\
HP-CLJ-CP2025A & 28 \\
HP-JL-CP1518 & 28 \\
Lexmark-E260D & 28 \\
OKI-C330 & 28 \\
Samsung-CLP315 & 28 \\
\end{tabular}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{neighbor}
	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest)}
\label{fig:neighbor}   
\end{center} 
\end{figure}

@@

>>>>

%%% PREAMBLE - Do not touch %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,twocolumn,letterpaper]{article}
%%\usepackage[ansinew]{inputenc}
\usepackage[latin1,utf8]{inputenc}
\usepackage[portuges,brazil,english]{babel}
\usepackage{model}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{appendix}
\input{abaco}

@@

\begin{table*}
\caption{Printers used in this work}
\label{tab:printers}
\begin{center}
    \begin{tabular}{ | c | c | c | c |}
    \hline
Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
Brother-HL4070CDW & 28 & 252 & 252\\
Canon-D1150 & 28 & 252 & 252\\
Canon-MF3240 & 28 & 252 & 252\\
Canon-MF4370DN & 27 & 252 & 252 \\
HP-CLJ-CP2025A & 28 & 250 & 250\\
HP-JL-CP1518 & 0 & 0 & 0\\
Lexmark-E260D & 0 & 0 & 0\\
OKI-C330 & 0 & 0 & 0\\
Samsung-CLP315 & 0 & 0 & 0 \\
\hline
    \end{tabular}
\end{center}    
\end{table*}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{neighbor}
	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest).}
\label{fig:neighbor}   
\end{center} 
\end{figure}

@@

\appendix
